---
title: "cp8_assignment_instructions"
author: "Aidan O'Hara"
date: "2023-08-22"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

```


## Exercise 1
Run `?anscombe`, briefly research who Anscombe was and write a short description, assigned to the variable `whoWasAnscombe`

## Exercise 2

Use sapply to calculate the mean and variance of columns y1-y4 in `anscombe`. Assigned to `anscombeMeans` and `anscombeVar` respectively.

Why is this response problematic?

## Exercise 3
run the following code in your script

```{r}
anscombe_tidy <- anscombe %>% 
  pivot_longer(x1:y4) %>%
  group_by(name) %>%
  # Add a unique ID number to each group
  mutate(row = row_number()) %>%
  # Split the column at the first appearance of a number
  separate(name, into = c('xy','group'), sep = "(?<=[a-zA-Z])\\s*(?=[0-9])") %>%
  pivot_wider(names_from = xy, values_from = value) %>%
  select(-row)
```

## Exercise 4
Finally, lets make a ggplot!  Within `aes` assign x to x and y to y, use `anscombe_tidy` data to generate a plot with `geom_point()`.  Assign your plot to `firstGGplot`.

## Exercise 5
Lets add some specifics about `group` to `shape` and `color`. First, assigned to `colorPlot`, assign `group` to `color` within your `aes()`.  Next, assigned to `shapePlot`, assign `group` to `shape` within `aes()`.  Finally, assigned to `greatPlot`, assign `group` to both `shape` and `color`.

## Exercise 6
Now to draw each `group` in a separate set of axis, use the facet_wrap function, specify that your `facet_wrap` makes 2 rows.
Add the `facet_wrap` to `greatPlot` from before, updating `greatPlot`.

Like this:
`greatPlot <- greatPlot + facet_wrap()`

## Exercise 7
Lets add a line of best fit to each `group`!  We'll again update our `greatPlot`, this time adding the `stat_smooth` function.

## Exercise 8
IN every plot you make, label everything!  Lets add labels to our `greatPlot` using the `labs` function.  Updating your `greatPlot` just like before.  
Be sure you label `x`, `y`, `title`, `subtitle`, `caption`, and `color`.

## Exercise 9
Finally, add `theme_minimal(`) to your `greatPlot`, assign the new plot to `bestPlot`.

